Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-29 report/report.tex
Analysis conclusions. Restructure collision cases presentation

% REPORT
% TODO: Proposed fixing algorithm: building-road
% TODO: Proposed fixing algorithm: road-road
% TODO: Mention propagation of error, have to include all the edited features in the next pass
% TODO: Proof read report

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_cases}
    \caption{The 5 identified cases over feature overlap. Top left: A building lies in paralel with a road, and the distance between the two is smaller than the minimum width of the road. Top right: A road shares a node with a building. Middle: A road is intersecting with certain building features. Bottom left: Two roads have a minimum distance that is smaller than the sum of the minimum widths of both roads. Bottom right: Two roads share a node, and a subsequent node in one road lies within the minimum width of the other road.}
    \label{fig:space}
\end{figure}

>>>>

% REPORT
% TODO: Proposed fixing algorithm: building-road
% TODO: Proposed fixing algorithm: road-road
% TODO: Proof read report

@@

\subsection{Feature overlap}

After visual inspection of the cases where features collide, it was determined that all collision occurences can be almost exclusively classified into one of five categories:

\begin{enumerate}
\item Case 1: A building lies in paralel with a road, and the distance between the two is smaller than the minimum width of the road.
\item Case 2: A road shares a node with a building.
\item Case 3: A road is intersecting with certain building features.
\item Case 4: Two roads have a minimum distance that is smaller than the sum of the minimum widths of both roads. 
\item Case 5: Two roads share a node, and a subsequent node in one road lies within the minimum width of the other road.
\end{enumerate}

Each case is exemplified in figure X. %{TODO}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_cases}
    \caption{The 5 identified cases over feature overlap. Top left: Case 1. Top right: Case 2. Middle: Case 3. Bottom left: Case 4. Bottom right: Case 5.}
    \label{fig:space}
\end{figure}

Propagation of error, have to include all the edited features in the next pass
